Tweedie in TMB

### 2019-02-20 analysis/tweedie-TMB.Rmd
Add profile examples

## Get parameter uncertainties and convergence diagnostics
sdr <- sdreport(obj)
sdr
```

>>>>

## Get parameter uncertainties and convergence diagnostics
sdr <- sdreport(obj)
sdr

## Get likelihood profiles for individual parameters:
a_profile <- tmbprofile(obj, "a")
b_profile <- tmbprofile(obj, "b")

plot(a_profile)
plot(b_profile)
confint(a_profile)
confint(b_profile)
```
